---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edbuildmapr

<!-- badges: start -->
<!-- badges: end -->

The goal of `edbuildmapr` is to simplify the use of school district shapefiles. The package import US
  Census Bureau, Education Demographic and Geographic Estimates Program, Composite School District
  Boundaries Files for 2013-2018 with the option to attach EdBuild's master dataset of school district
  finance, student demographics, and community economic indicators for every school district in the United
  States. The master dataset is built from the US Census, Annual Survey of School System Finances (F33) and
  joins data from the National Center for Education Statistics, Common Core of Data; the US Census,
  Small Area Income and Poverty Estimates; and the US Census, Education Demographic and Geographic 
  Estimates. Additional functions in the package create a dataset of all school district neighbors as 
  either a dataframe or a shapefile and maps of selected districts at the state or neighbor level
  symbolized by a selected variable in EdBuild's master dataset. For full details about EdBuild's data
  processing please see EdBuild (2020) [Methodology](https://data.edbuild.org/). 

## Installation

You can install the released version of edbuildmapr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("edbuildmapr")
```

## Example

To import school district spatial data for all districts with EdBuild's master data: 

```{r example}
library(edbuildmapr)
## import school district shapefile for the year 2018 with EdBuild's master dataset attached. 
sd_shp_18 <- sd_shapepull("2018", with_data = TRUE)

str(sd_shp_18)
```

## Authors
* Megan Brodzik (meganbrodzik@edbuild.org), maintainer
* Cecilia Depman (cecilia.depman@gmail.com), author 
* Sara Hodges (sara.hodges@gmail.com), author
